Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-31 Paper/MSRChallenge2017.tex
fixed a typo
minor changes on last proof-read

This previous work has focused on the predicted acceptance of open source \emph{pull
requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} builds
in a single project~\cite{Hassan06,Kwan11,Wolf09}. 
By contrast,  we are interested in analyzing contribution quality 
in \emph{continuous integration} across multiple open source projects.  While 
pull request
quality is ultimately determined through manual inspection, continuous
integration uses test cases to automatically assess commit quality,
and thus may provide different quality predictors. 
We investigate the factors related to continuous integration build success
across open source projects.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contribution's quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

@@

\vspace{1ex}
\noindent\textbf{Technical Factors.} We collected technical factors from the 
Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
We extracted the following technical attributes to proxy a commit's
complexity: 
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn, changed lines of code.
\item Files added by this commit.
\item Files modified by this commit.
\item Tests added by this commit.
\item Tests deleted by this commit.
\item Total source files in project at the time of the commit.
\item Number of source lines of code in the project at
	the time of the commit.
\item Travis status, or status of the Travis build integration.
\end{itemize}

@@

74.43\% of the builds in the reduced data set were successful, and thus a naive
classifier that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second \emph{balanced} data set by randomly 
sub-sampling the successful builds until the two build status were
equal, through a process known as downsampling. We downsampled the entire
data set and then trained decision tree classifiers on both.  We validated the
classifiers with cross-validation. Since the cross-validation is stratified, the
50-50 proportion is maintained through the training and testing folds for the
downsampled data. We present results for both
data sets in Section~\ref{sec:successClassification},  and only the full data 
set in Sections~\ref{sec:core} and \ref{sec:followerSuccess}.

@@

The decision tree results suggested that core team membership is
important to classifying build success (in supplemental material), and thus 
we investigated the question
directly. 
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set; 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set,
and 64.70\% (25479/39381) of the builds passed.  The difference in success rate
is statistically significant (the p-value from a Fisher exact
test is 0.0000), suggesting that it is extremely unlikely to have occurred by
chance. Thus, in our dataset, core team 
members are more
likely to have a successful build integration than non-core team developers, likely
because core team members are naturally more familiar with the 
codebase.

@@

%\paragraph{Internal validity}
In the study, we use Weka, a well known machine-learning toolkit,
to analyze our data.
Like all tools, Weka may contain bugs. 
Nonetheless, it is a community tested open source tool, which mitigates threats to 
internal validity. We also release our scripts, data, and decision tree 
results in the study.\footnote{https://github.com/squaresLab/MSR-challenge-2017}

@@

We have analyzed how technical and social factors can be used to
predict high quality open source contributions, measured by continuous
integration build success.  We found social factors improve predictions of build 
success; technical factors led to a 14\% increase in predictive power, and 
adding social factors led to another 12\% increase.

Overall, we conclude that social attributes proxying experience, such as whether
the developer is a core project contributor,
noticeably influence build success prediction, especially on the downsampled
data. 
%These results suggest that social factors
%are significant predictors when
%evaluating the predictive power of build commit success.
%
In particular, core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits may not be
scrutinized as closely as core team member commits before the integration build 
tests,
although further study is required to draw definitive
conclusions.
%
Likewise, developers with more followers are more
likely to pass the build.
Developers with 1000+ followers were more than 10\% more succesful in their
builds compared to
developers with no followers.  This suggests that open source developers with
high quality commits may be more
likely to have a large number of followers.

>>>>

This previous work has focused on the predicted acceptance of open source \emph{pull
requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} (CI) builds
in a single project~\cite{Hassan06,Kwan11,Wolf09}. 
By contrast,  we are interested in analyzing contribution quality 
in \emph{continuous integration} across multiple open source projects.  While 
pull request
quality is ultimately determined through manual inspection, continuous
integration uses test cases to automatically assess commit quality,
and thus may provide different quality predictors. 
We investigate the factors related to continuous integration build success
across open source projects.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contribution's quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

@@

\vspace{1ex}
\noindent\textbf{Technical Factors.} We collected technical factors from the 
Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
We extracted the following technical attributes to proxy a commit's
complexity: 
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn (changed lines of code).
\item Files added by this commit.
\item Files modified by this commit.
\item Tests added by this commit.
\item Tests deleted by this commit.
\item Total source files in project at the time of the commit.
\item Number of source lines of code in the project at
	the time of the commit.
\item Travis status, or status of the Travis build integration.
\end{itemize}

@@

74.43\% of the builds in the reduced data set were successful, and thus a na\"ive
classifier that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second \emph{balanced} data set by randomly 
sub-sampling the successful builds until the two build status were
equal, through a process known as downsampling. We downsampled the entire
data set and then trained decision tree classifiers on both.  We validated the
classifiers with cross-validation. Since the cross-validation is stratified, the
50-50 proportion is maintained through the training and testing folds for the
downsampled data. We present results for both
data sets in Section~\ref{sec:successClassification},  and only the full data 
set in Sections~\ref{sec:core} and \ref{sec:followerSuccess}.

@@

The decision tree results suggested that core team membership is
important to classifying build success (in supplemental material), and thus 
we investigated the question
directly. 
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set; 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set,
and 64.70\% (25479/39381) of the builds passed.  The difference in success rate
is statistically significant (the p-value from a Fisher exact
test is 0.0000), suggesting that it is extremely unlikely to have occurred by
chance. Thus, in our dataset, core team 
members 
have a successful build integration more often than non-core team 
developers, likely
because core team members are naturally more familiar with the 
codebase.

@@

%\paragraph{Internal validity}
In the study, we use Weka, a well known machine-learning toolkit,
to analyze our data.
Like all tools, Weka may contain bugs. 
Nonetheless, it is a community tested open source tool, which mitigates threats to 
internal validity. We also release our scripts, data, and decision tree 
results.\footnote{https://github.com/squaresLab/MSR-challenge-2017}

@@

We have analyzed how technical and social factors can be used to
predict high quality open source contributions, measured by continuous
integration build success.  We found social factors improve predictions of build 
success, technical factors led to a 14\% increase in predictive power, and 
adding social factors led to another 12\% increase.

Overall, we conclude that social attributes proxying experience, such as whether
the developer is a core project contributor,
noticeably influence build success prediction, especially on the downsampled
data. 
%These results suggest that social factors
%are significant predictors when
%evaluating the predictive power of build commit success.
%
In particular, core team members are
more likely to have the build integration pass than non-core team members.  This
result provides evidence that non-core team member commits may not be
scrutinized as closely as core team member commits before the integration build 
tests,
although further study is required to draw definitive
conclusions.
%
Likewise, developers with more followers are more
likely to pass the build.
Developers with 1000+ followers were more than 10\% more successful in their
builds compared to
developers with no followers.  This suggests that open source developers with
high quality commits may be more
likely to have a large number of followers.
